---
title: "Project3_Updated"
author: "Rahul Abraham"
date: "April 6, 2020"
output: html_document
---

```{r}
insurance <- read.csv("insurance.csv")
insurance$Customer <- NULL
insurance$State <- as.factor(insurance$State)
insurance$Customer.Lifetime.Value <- as.numeric(insurance$Customer.Lifetime.Value)
insurance$Income <- as.numeric(insurance$Income)
insurance$Monthly.Premium.Auto <- as.numeric(insurance$Monthly.Premium.Auto)
insurance$Months.Since.Last.Claim <- as.numeric(insurance$Months.Since.Last.Claim)
insurance$Number.of.Open.Complaints <- as.numeric(insurance$Number.of.Open.Complaints)
insurance$Number.of.Policies <- as.numeric(insurance$Number.of.Policies)
insurance$Total.Claim.Amount <- as.numeric(insurance$Total.Claim.Amount)
insurance$Months.Since.Policy.Inception <- as.numeric(insurance$Months.Since.Policy.Inception)
insurance$Effective.To.Date <- NULL
insurance$Gender <- as.factor(ifelse(insurance$Gender == "M", "Male", "Female"))


str(insurance)
```



Exploring Data
```{r}
options(scipen=999)

plot(x = insurance$Income, y = insurance$Total.Claim.Amount, xlab = "Income", ylab = "Total Claim Amount")

plot(x = insurance$Policy.Type, y = insurance$Total.Claim.Amount, xlab = "Gender", ylab = "Total Claim Amount")

plot(x = insurance$State, y = insurance$Total.Claim.Amount, xlab = "State", ylab = "Total Claim Amount")

plot(x = insurance$Coverage, y = insurance$Total.Claim.Amount, xlab = "Gender", ylab = "Total Claim Amount")
```


Linear Model
```{r}
Mod1 <- lm(Total.Claim.Amount ~., data = insurance)

summary(Mod1)
```
Model shows that coverage type, education, gender, income, housing type, marital status, monthly premiums, type of renewal policy and the car being a sports car are significant variables. Surprisingly, customer lifetime value is not significant in predicitng a customers total claim amount.




Linear Model with only significant variables and interactions
```{r}

Mod2 <- lm(Total.Claim.Amount ~ Response + Coverage + Education + EmploymentStatus + Gender + Income + Location.Code + Marital.Status + Monthly.Premium.Auto + Vehicle.Class + Marital.Status*Location.Code + Education*Marital.Status + Marital.Status*Location.Code + EmploymentStatus*Education + Income*Marital.Status + Income*Coverage + Gender*Income , data = insurance)

summary(Mod2)
```
People with premium insurance coverage tend to have much higher total claims costs. Simiarly, people with masters degrees tend to have higher total claims costs as well. Retired people have lower total claims costs, but unemployed people have higher total claims costs. SImilarly, men tend to have higher claims costs than women, and an increase an income tends to have a higher claims costs. Similarly, people in the suburbs tend to have much higher claims costs than people from urban areas and they more than from rural areas. Single people also tend to have higher claims costs. Similarly people who pay more expensive auto premiums have higher total claims costs. Among people with masters degrees, those who are married tend to have lower total claims costs. The

